Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2021-09-01 Manuscript/HI_Model_supp.Rmd
updated supplementary files

```{r fig.align = 'center', out.width = "99%", fig.cap = "Supplemental - Moisture zones of the seven main Hawaiian Islands, adapted from Jacobi \\textit{et al.} (2017)."}

@@

```{r fig.align = 'center', out.width = "95%", fig.cap = "Supplemental - Annual area burned by wildland fire in the State of Hawaiʻi from 1999-2019, summed by year across the seven main Hawaiian Islands (A) and within each of the four largest islands (B). The dashed horizontal line in (A) represents the median area burned from 1999-2019."}

@@

Changes in NPP due to projected changes in climate were estimated using a set of temporal NPP multipliers representing the proportion of contemporary (2010) NPP (supplemental Figure 5) occuring in each simulation at mid-century and end-of-century under RCPs 4.5 and 8.5. We calculated temporal NPP multipliers by first estimating NPP for each simulation cell based on contemporary climate (supplemental figure 3) and projected future climates (supplemental figure 4) using empirical relationships between NPP and climate [@schuur_productivity_2003; @del_grosso_global_2008]. We then divided contemporary NPP estimates by future NPP estimates in each simulation cell to derive mid-century and end-of-century temporal multipliers (supplemental figure 6). Annual increments were calculated by dividing mid-century and end-of-century temporal multipliers by the number of intervening years.  
```{r}
library(kableExtra)
ibisnpp <- read.csv("IBISnpp_wide.csv", stringsAsFactors = FALSE)
kbl(ibisnpp, booktabs = T, caption = "Supplemental - Mean IBIS-derived NPP values by Land Cover and Moisture Zone, in kg of C per square meter per year.") %>%
   add_header_above(c(" ", "NPP by Moisture Zone" = 3))
```
```{r fig.align = 'center', out.width = "80%", fig.cap = "Supplemental - Stationary spatial NPP multipliers (top panel) and initial NPP based on the product of mean IBIS-derived NPP values (supplemental Table 1) and stationary spatial NPP multipliers (above). Developed and Barren land cover types are excluded from both maps."}
knitr::include_graphics("./fig_images/figS5_initialNPP.png")
```
```{r fig.align = 'center', out.width = "80%", fig.cap = "Supplemental - Temporal NPP multipliers for the year 2100 under RCP 4.5 (top panel) and RCP 8.5 (bottom panel). Temporal NPP multipliers represent the relative amount of initial (2010) NPP that occurs in each pixel in the year 2100 under each of two representative concentration pathways (RCPs) for atmospheric carbon dioxide. Developed and Barren land cover types are excluded from both maps."}
knitr::include_graphics("./fig_images/figS6_tempNPPmulti.png")
```
### *Land Cover Change*
Projections of total land area covered by each of five land cover classes (Agriculture, Developed, Forest, Grassland and Shrubland) summed by year and Monte Carlo iteration across the seven main Hawaiian Islands for each of two land use scenarios (low and high) are displayed in supplemental Figure 7. The decline in agricultural land between 2020 and 2040 in the low land use scenario led directly to the increase in Forest, Grassland, and Shrubland land area over the same time period. Changes in agricultural land area over time in the high land use scenario reflect a balance between high rates of agricultural contraction and high rates of agricultural expansion.     
```{r fig.align = 'center', out.width = "90%", fig.cap = "Supplemental - Projections of total land area by year for Agriculture, Developed, Forest, Grassland and Shrubland land cover classes in the Hawaiian Islands under low and high land use change scenarios for the period 2010-2100. Solid lines represent the mean of 30 Monte Carlo realizations and shaded areas represent minimum and maximum Monte Carlo values."}
knitr::include_graphics("./fig_images/figS7_StateClassArea.png")
```
## References

>>>>

```{r fig.align = 'center', out.width = "90%", fig.cap = "Supplemental - Moisture zones of the seven main Hawaiian Islands, reproduced from Jacobi \\textit{et al.} (2017). Credit: U.S. Geological Survey."}

@@

```{r fig.align = 'center', out.width = "99%", fig.cap = "Supplemental - Annual area burned by wildland fire in the State of Hawaiʻi from 1999-2019, summed by year across the seven main Hawaiian Islands (A) and within each of the four largest islands (B). The dashed horizontal line in (A) represents the median area burned from 1999-2019."}

@@

Changes in NPP due to projected changes in climate were estimated using a set of temporal NPP multipliers representing the proportion of contemporary (2010) NPP (supplemental Figure 5) occuring in each simulation at mid-century and end-of-century under RCPs 4.5 and 8.5. We calculated temporal NPP multipliers by first estimating NPP for each simulation cell based on contemporary climate (supplemental figure 3) and projected future climates (supplemental figure 4) using empirical relationships between NPP and climate [@schuur_productivity_2003; @del_grosso_global_2008]. We then divided contemporary NPP estimates by future NPP estimates in each simulation cell to derive mid-century and end-of-century temporal multipliers (supplemental figure 6). Annual increments were calculated by dividing mid-century and end-of-century temporal multipliers by the number of intervening years.  
```{r}
library(kableExtra)
ibisnpp <- read.csv("IBISnpp_wide.csv", stringsAsFactors = FALSE)
kbl(ibisnpp, booktabs = T, caption = "Supplemental - Mean IBIS-derived NPP values by Land Cover and Moisture Zone, in kg of C per square meter per year.") %>%
   add_header_above(c(" ", "NPP by Moisture Zone" = 3))
```
```{r fig.align = 'center', out.width = "80%", fig.cap = "Supplemental - Stationary spatial NPP multipliers (top panel) and initial NPP based on the product of mean IBIS-derived NPP values (supplemental Table 1) and stationary spatial NPP multipliers (above). Developed and Barren land cover types are excluded from both maps."}
knitr::include_graphics("./fig_images/figS5_initialNPP.png")
```
```{r fig.align = 'center', out.width = "80%", fig.cap = "Supplemental - Temporal NPP multipliers for the year 2100 under RCP 4.5 (top panel) and RCP 8.5 (bottom panel). Temporal NPP multipliers represent the relative amount of initial (2010) NPP that occurs in each pixel in the year 2100 under each of two representative concentration pathways (RCPs) for atmospheric carbon dioxide. Developed and Barren land cover types are excluded from both maps."}
knitr::include_graphics("./fig_images/figS6_tempNPPmulti.png")
```
### *Land Cover Change*
Projections of land area covered by each of five land cover classes (Agriculture, Developed, Forest, Grassland and Shrubland) summed by year and Monte Carlo iteration across the seven main Hawaiian Islands for each of two land use scenarios (low and high) are displayed in supplemental Figure 7. The decline in agricultural land between 2020 and 2040 in the low land use scenario led directly to the increase in Forest, Grassland, and Shrubland land area over the same time period. Changes in agricultural land area over time in the high land use scenario reflect a balance between high rates of agricultural contraction and high rates of agricultural expansion.

```{r fig.align = 'center', out.width = "99%", fig.cap = "Supplemental - Projections of total land area by year for Agriculture, Developed, Forest, Grassland and Shrubland land cover classes in the Hawaiian Islands under low and high land use change scenarios for the period 2010-2100. Solid lines represent the mean of 30 Monte Carlo realizations and shaded areas represent minimum and maximum Monte Carlo values."}
knitr::include_graphics("./fig_images/figS7_StateClassArea.png")
```
## References
